\documentclass[a4paper,onesided,12pt]{report}
\usepackage{styles/fbe_tez}
\usepackage[utf8]{inputenc} % To use Unicode (e.g. Turkish) characters
\renewcommand{\labelenumi}{(\roman{enumi})}
\usepackage{amsmath, amsthm, amssymb}
% Some extra symbols
\usepackage[bottom]{footmisc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{longtable}
\graphicspath{{figures/}} % Graphics will be here

\usepackage{multirow}
\usepackage{subfigure}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
%\pagestyle{empty}
%\includeonly{introduction} % To only process the given file


\newtheorem{thm}{Theorem}[chapter]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}



% COVER PAGE
\title{AIRFLOW ESTIMATION FROM RESPIRATORY SOUNDS}
\turkcebaslik{SOLUNUM SESLERİNDEN SOLUK AKIŞI KESTİRİMİ}
\degree{B.S., Electrical \& Electronics Engineering, Boğaziçi University, 2013}
\author{İlhan Yıldırım}
\program{Electrical \& Electronics Engineering}
\subyear{2018}

% APPROVED BY PAGE
\supervisor{Prof. Yasemin Z. Kahya}
\cosuperi{Assist. Prof. İpek Şen}
%\cosuperii{Title and Name of Cosupervisor II}
\examineri{Prof. Murat Saraçlar}
\examinerii{Assoc. Prof. Rifat Koray Çiftçi}
%\examineriii{}
%\examineriv{}
%\examinerv{}
\dateofapproval{24.5.2018}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\@sect}{\underbar}{\underline}{}{}
\makeatother

\usepackage{tikz}
\usetikzlibrary{shapes, calc, shapes, arrows}
\DeclareMathOperator*{\argmin}{arg\,min}
\begin{document}
	
	\pagenumbering{roman}
	\makemstitle % M.S. thesis
	\makeapprovalpage
	\begin{acknowledgements}
		Acknowledgements come here...
	\end{acknowledgements}
	\begin{abstract}
		One page abstract will come here.  
	\end{abstract}
	\begin{ozet}
		Bir sayfa uzunluğunda özet gelecektir.
	\end{ozet}
	\tableofcontents
	\listoffigures
	\listoftables
	\begin{symbols}
		% The title will be typeset as "LIST OF SYMBOLS".
		%
		% Use a separate \sym command for each symbols definition.
		% First Latin symbols in alphabetical order
		
		\sym{$a_{ij}$}{Description of $a_{ij}$}
		\sym{$\mathbf{A}$}{State transition matrix of a hidden Markov model}
		% Then Greek symbols in alphabetical order
		\sym{}{}
		\sym{$\alpha$}{Blending parameter \textit{or} scale}
		\sym{$\beta_t(i)$}{Backward variable}
		\sym{$\Theta$}{Parameter set}
		\sym{ }{}
		
	\end{symbols}
	
	\begin{abbreviations}
		% Abbreviations in alphabetical order
		\sym{2D}{Two Dimensional}
		\sym{3D}{Three Dimensional}
		\sym{AAM}{Active Appearance Model}
		\sym{ASM}{Active Shape Model}
	\end{abbreviations}
	

\input{introduction}
\input{exp_setup_data}
\input{airflow_curve_estimation}
\input{phase_estimation_using_airflow}
\input{conclusion}
\bibliographystyle{styles/fbe_tez_v11}
\bibliography{references}

\end{document}