\documentclass[a4paper,onesided,12pt]{report}
\usepackage{styles/fbe_tez}
\usepackage[utf8x]{inputenc} % To use Unicode (e.g. Turkish) characters
\renewcommand{\labelenumi}{(\roman{enumi})}
\usepackage{amsmath, amsthm, amssymb}
 % Some extra symbols
\usepackage[bottom]{footmisc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{longtable}
\graphicspath{{figures/}} % Graphics will be here

\usepackage{multirow}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algorithmic}
%\pagestyle{empty}
%\includeonly{introduction} % To only process the given file

\newtheorem{thm}{Theorem}[chapter]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
% COVER PAGE
\title{Airflow Estimation From Respiratory Sounds}
\turkcebaslik{Solunum Seslerinden Soluk Akışı Kestirimi}
\degree{B.S., Electrical \& Electronics Engineering, Boğaziçi University, 2013}
\author{İlhan Yıldırım}
\program{Electrical \& Electronics Engineering}
\subyear{2017}

% APPROVED BY PAGE
\supervisor{Prof. Yasemin Z. Kahya}
\cosuperi{Assist. Prof. İpek Şen}
%\cosuperii{Title and Name of Cosupervisor II}
\examineri{Prof. Emin Anarım}
\examinerii{Assoc. Prof. Ali Emre Pusane}
\examineriii{Prof. Mehmed Özkan}
%\examineriv{}
%\examinerv{}
\dateofapproval{01.01.2017}

\begin{document}

\pagenumbering{roman}
\makemstitle % M.S. thesis
\makeapprovalpage
\begin{acknowledgements}
Acknowledgements come here...
\end{acknowledgements}
\begin{abstract}
One page abstract will come here.  
\end{abstract}
\begin{ozet}
Bir sayfa uzunluğunda özet gelecektir.
\end{ozet}
\tableofcontents
\listoffigures
\listoftables
\begin{symbols}
% The title will be typeset as "LIST OF SYMBOLS".
%
% Use a separate \sym command for each symbols definition.
% First Latin symbols in alphabetical order

\sym{$a_{ij}$}{Description of $a_{ij}$}
\sym{$\mathbf{A}$}{State transition matrix of a hidden Markov model}
% Then Greek symbols in alphabetical order
\sym{}{}
\sym{$\alpha$}{Blending parameter \textit{or} scale}
\sym{$\beta_t(i)$}{Backward variable}
\sym{$\Theta$}{Parameter set}
\sym{ }{}

\end{symbols}

\begin{abbreviations}
 % Abbreviations in alphabetical order
\sym{2D}{Two Dimensional}
\sym{3D}{Three Dimensional}
\sym{AAM}{Active Appearance Model}
\sym{ASM}{Active Shape Model}
\end{abbreviations}


\chapter{INTRODUCTION}
\label{chapter:introduction}
\pagenumbering{arabic}
Start with an introduction...

\chapter{EXPERIMENTAL SETUP AND DATA}
\label{chapter:introduction}
\pagenumbering{arabic}
Start with an introduction...

%\include{experiments_results}
\chapter{AIRFLOW CURVE ESTIMATION}
\label{chapter:airflow-curve-estimation}
Start with an introduction...
\section{Respiratory Sound Modelling}

\section{Literature Survey}

\section{Time Varying Autoregressive Modeling}
\subsection{Method}
\subsection{Tests and Results}

\section{Autoregressive Modeling with Overlapping Windows}
\subsection{Method}
\subsection{Tests and Results}

\section{Time - Frequency Analysis}
\subsection{Method}
\subsection{Tests and Results}

\section{Unified Estimations}
\subsection{Method}
\subsection{Tests and Results}


\chapter{AIRFLOW PHASE DETECTION}
\label{chapter:introduction}
Start with an introduction...

\section{Estimation of Periods}
\section{Estimation of Change Point Locations}
\section{Feature Extraction}

\section{Results}

\chapter{CONCLUSION}
\label{chapter:conclusion}

The conclusions of the thesis should come
here.
% \nocite{NewEntry1,NewEntry2,NewEntry3,NewEntry4,NewEntry5,
% NewEntry6,
% NewEntry7,NewEntry8,NewEntry9,NewEntry10,NewEntry11,NewEntry12}

%\cite{*}
\bibliographystyle{styles/fbe_tez_v11}
\bibliography{references}

\appendix
\chapter{APPLICATION}
The appendices start here.

\end{document}